---
title: "100-well-demulti"
author: "Mac Campbell"
date: "2022-10-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

The point of this file is to set up a well demultiplex of inline barcode RAD data.

# Organization notes
I have made a .gitignore file that contains:    

```{sh}
head .gitignore
```

Anything put in data, outputs, bams or ends with .html won't be synced via github.     



## Data Location    

`/home/amilzz/projects/LCT/BMAG072/raw2/lane3`     
`/home/amilzz/projects/LCT/BMAG072/raw2/lane4`     

Expect to work the best: /home/amilzz/projects/LCT/BMAG072/raw2/lane3/LibPlate10_WWH2_R1.fastq      

I'll set up on FARM like so:       

`(base) maccamp@farm:~$ git clone https://github.com/amilzz/amilzz`     
`(base) maccamp@farm:~$ cd amilzz/`       
`(base) maccamp@farm:~/amilzz$ mkdir data`      
`(base) maccamp@farm:~/amilzz$ mkdir data/lane3`      
`(base) maccamp@farm:~/amilzz$ mkdir data/lane4`
`(base) maccamp@farm:~/amilzz$ cd data/lane3/`    
`(base) maccamp@farm:~/amilzz/data/lane3$ ln -s /home/amilzz/projects/LCT/BMAG072/raw2/lane3/LibPlate10_WWH2_R1.fastq `      
`(base) maccamp@farm:~/amilzz/data/lane3$ ln -s /home/amilzz/projects/LCT/BMAG072/raw2/lane3/LibPlate10_WWH2_R2.fastq `      
`(base) maccamp@farm:~/amilzz/data/lane3$ cd ../lane4`
`(base) maccamp@farm:~/amilzz/data/lane4$ ln -s /home/amilzz/projects/LCT/BMAG072/raw2/lane4/LibPlate10_WWH2_R1.fastq`      
`(base) maccamp@farm:~/amilzz/data/lane4$ ln -s /home/amilzz/projects/LCT/BMAG072/raw2/lane4/LibPlate10_WWH2_R2.fastq`    

This will have two subdirs in data for each lane, working from amilzz, I can combine these with cat.     
````{sh, eval=FALSE}

mkdir data/combined
#this is an inefficient way to do this, but basically:
cat data/lane3/LibPlate10_WWH2_R1.fastq data/lane4/LibPlate10_WWH2_R1.fastq > data/combined/LibPlate10-combined-R1.fastq
#yawn. 
cat data/lane3/LibPlate10_WWH2_R2.fastq data/lane4/LibPlate10_WWH2_R2.fastq > data/combined/LibPlate10-combined-R2.fastq &
```


# Splitting one way

Ensieh put together a set of scripts.  

`(base) maccamp@farm:~/amilzz/data/combined$ ls *R1*.fastq > listR1`    
`(base) maccamp@farm:~/amilzz/data/combined$ ls *R2*.fastq > listR2`     
`ls Lib*R1* | sed "s/-R1//g" | sed "s/\.fastq//g" | paste listR1 listR2 - > flist`      

flist looksl like this:      
`LibPlate10-combined-R1.fastq	LibPlate10-combined-R2.fastq	LibPlate10-combined`      

Now, we need all the scripts it is going to use in the directory it is executed in and a slumrout file.    
`mkdir slurmout`
`ln -s ../../scripts/*.* .`   



Don't need a bunch of these scripts.         

` rm prerun_wellsplit.sh prerun_wellsplit.txt run_wellsplit.txt run_BestRadSplit.txt run_BestRadSplit_PstI.*`      

`(base) maccamp@farm:~/amilzz/data/combined$ sbatch run_wellsplit.sh flist `       


Ensieh notes:    
_0_ in the current directory, make a directory called "slurmout": mkdir slurmout # to put the slurm files in different directory       
_1_  run "prerun_wellsplit.sh":  sbatch prerun_wellsplit.sh     
_2_  run "run_wellsplit.sh":  sbatch run_wellsplit.sh flist 

I didn't follow these because the naming of the files wouldn't do. So I made a "flist" file myself.    

   

# Batch combining plates

One way is to put all the commands in a text file and execute with parallel.     

That is a file that looks like:

```{sh}
head 100.2-batch-combine-example.sh
```

This can be executed like so on the FARM:    

```{sh, eval=FALSE}
srun -p high -t 2:00:00 --nodes=1 parallel -j 2 < 100.2-batch-combine-example.sh > data/combined/std.out 2>data/combined/std.err &

```

-j indicates the number of commands to run in parallel, so adjust accordingly.


# Renaming

This can be done at many different times. Using the demultiplexed files in data/combined I'll move them to data/split. These also can be made as links.     

```{r}
meta<-read_csv("meta/WWH2_libraryPlate10.csv")
meta
```

Our files look like LibPlate10-combined_RA_GGAAACATCGTGCAGG.fastq and so on. I'll put them in a directory data/align on FARM. (mkdir data/align)

```{r}
forward<-meta %>% 
  mutate(Command=paste0("mv data/combined/LibPlate10-combined_RA_GG",SampleIndex_WellBarcodes,
                                        "TGCAGG.fastq data/align/",SampleID,"_RA.fastq")) %>%
  select(Command)

forward
```

Combining with reverse.     
```{r}
reverse<-meta %>% 
  mutate(Command=paste0("mv data/combined/LibPlate10-combined_RB_GG",SampleIndex_WellBarcodes,
                                        "TGCAGG.fastq data/align/",SampleID,"_RB.fastq")) %>%
  select(Command)

write_tsv(bind_rows(forward,reverse), "100.3-batch-rename.sh")
reverse
```

